---
title: "Day 1 - Practice"
author: "Your Name Here | and your email address"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

# Day 1 - Practice 

## Overview 
You are a newly hired data scientist working for a telecommunication company like Verizon or ATT. You have been tasked to identify which customers are likely to "churn". Customer churn, also known as customer attrition, occurs when customers stop doing business with a company or stop using a company’s services. 

## Libraries & Packages 

1. Install skimr package - skim provides a nice summary of a dataset 
2. Install janitor package - cleans up column names 
3. Load the following libraries.  
- tidyverse  
- skimr 
- janitor 

Copy this into the code block  

library(tidyverse)  
library(skimr)  
library(janitor)  


```{r}

```

## Load Dataset 

churn.csv use head to print out the first 10 records. 

churn <- read_csv("data/churn.csv") 
head(churn,10)

```{r}



```

## Clean up Column names 

The janitor package provides a neat function clean_names() which will convert spaces to underscores, lowercase everything, deal with special characters like quotes, hypyens, and others. 

churn <- churn %>%  
  clean_names()  

head(churn,10)  

```{r}

```

## Count rows and columns with nrow and ncol 

- nrow() - number of rows  
- ncol() - number of columns  

nrow(churn)  
ncol(churn)  

```{r}

```

## Use skim() function 

The core function of skimr is skim(), which is designed to work with (grouped) data frames, and will try coerce other objects to data frames if possible. Like summary(), skim()’s method for data frames presents results for every column; the statistics it provides depend on the class of the variable.


churn %>%  
  skim()  

```{r}

```


## Skim group_by churn 

group by works just like it's name it simply groups things so that they can be analyzed independantly


churn %>%  
  group_by(churn) %>%  
  skim()  

```{r}

```

## Summarize churn column 

how many accounts are churners? 

churn %>%  
  group_by(churn) %>%  
  summarize(n = n())  

```{r}

```

## can i get that in Percentage 

What is the % of churner non-churner? 

we use mutate to add varaibles from formulae 

churn %>%  
  group_by(churn) %>%  
  summarize(n = n()) %>%  
  mutate(pct = n/sum(n)  )  

```{r}


```


## Make a Histogram of day_calls

using hist - ok this isn't particulary attractive graph  

here is the code 
hist(churn$day_calls)  

```{r}

```

### Lets make a better looking chart 

ggplot makes modern plots and graphs instead of the base graph packages which look like the 1980s  

lets use ggplot and geom_histogram to make a histogram of day_calls 

ggplot(churn, aes(x=day_calls)) +
  geom_histogram( stat="count")

```{r}

```

## Add a title 

we need to tell people what our chart is all about 

ggplot(churn, aes(x=day_calls)) +  
  geom_histogram( stat="count") +   
  ggtitle("Histogram of Day Mins")  

```{r}



```

## Add a Fill Aestetic 

Fills color our graphs 

ggplot(churn, aes(x=day_calls, fill=churn)) +   
  geom_histogram( stat="count") +   
  ggtitle("Histogram of Day Mins")  

```{r}



```

## Fact Wrap by intl_plan

facet wrap makes the same graph for each level in the facet, you do this with the function face_wrap() and reference the column with a sqiggly ~ column name 

sample code :  

ggplot(churn, aes(x=day_calls, fill=churn)) +  
  geom_histogram( stat="count") +   
  ggtitle("Histogram of Day Mins") +  
  facet_wrap(~intl_plan)  

```{r}

```

## Now you Try 

see if you can do the following, simply insert a new code block and try these. 

1. group_by state, and churn, create counts 
2. make a histogram of day_charge using hist
3. make a histogream of day_charge using ggplot 
4. craete a new table by grouping by area_code and counting n() 

```{r}

```


